---
title: "BiocSwirl_courses"
author: "EL Strand"
date: "1/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Clears workspace. 
```{r}
rm(list=ls())
```

Loading libraries. I had trouble downloading devtools so I updated 'processx' package, installed 'usethis', and re-ran the install devtools function. Seems to have fixed this. 
```{r}
install.packages("devtools")
library(devtools)

devtools::install_github("biocswirl-dev-team/BiocSwirl") # selected '1' to update all; 'Yes' to install that need compilation; 'Yes' to install from C/C++/Fortran: 'brio'. This install took awhile. 
library(BiocSwirl)
```

```{r, eval = FALSE}
# list all available BiocSwirl courses
list_courses()
# install selected course. 
# copy name from output of list_courses()
load_course(course ='RNAseq')
```

To start the course environment, excute the command below. No parameters are necessary. The command will start an interactive environment that will allow you to navigate to your course.
```{r, eval = FALSE}
start_course()
```

# RNASeq

## Installing packages 
Fully update R and RStudio prior to starting. 

```{r}
install.packages("pheatmap")
library(pheatmap)

install.packages("latticeExtra")
library(latticeExtra)

install.packages("acepack")
library(acepack)

install.packages("Hmisc")
library(Hmisc)

install.packages("BiocManager")

BiocManager::install("DESeq2") #select 'a' for all
library(DESeq2)
```
Opening the DESeq2 documentation and cite the authors. 
```{r}
browseVignettes("DESeq2")

citation("DESeq2")
```

## Fastq download 
What additional information does a fastq file contain? "quality information"

Look up the GEO accession GSE147507 on the NCBI website. What is the title of that accession?
> https://www.ncbi.nlm.nih.gov/geo/
> Input 'GSE147507' in search bar.
> https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE147507
> Title = Transcriptional response to SARS-CoV-2 infection

Which data files can you find directly on the page of the GSE147507 accession? "Raw count data"

How many samples for the human cell line NHBE are there in this dataset? Got stuck none of these answers work!! 


```{r}

```


